\papertitle

### 2012-10-12 manuscript.tex
Fix bibtex errors

Autonomous control of flapping winged MAVs is a complex undertaking because of
the non-linear flight dynamics as presented
in~\cite{humbert:dipteran2,cheng:tandrdamping}. Although the dynamics of
flapping-winged flight can be averaged with respect to the wingbeat period as
presented in~\cite{Schenato:flightcontrol,cheng:tandrdamping}, we develop a
linear, one-dimensional model to predict the behavior of the system, similar
to~\cite{Shigeoka:ornithopter}. In addition to the nonlinearities, the system
is underactuated due to size constraints. Many of the methods for controlling
these platforms make extensive use of GPS in outdoor environments [CITATIONS]
and expansive motion capture systems in indoor environments. While operating
indoors, using GPS to estimate the pose of the MAV is not possible, and motion
capture requires expensive and stationary modification of the environment. The
power and payload limits on MAVs make on-board sensing difficult, so
multi-agent cooperative control schemes are apt solutions.

Many of the control laws that previous researches have developed from the
dynamic models of flapping-winged flight, such as periodic forcing and other
control methods as describesd in~\cite{doman:dynamics,
khan:longitudinal_control, leonard:averaging}, are computationally complex and
require powerful on-board computing. In our work, we develop a simpler, less
computationally intensive method of control for negotiating narrow passages.

@@

\subsubsection{Reachability Model}
\label{sec:visual_servoing}
%TODO make these span the page, with identical scales/style

>>>>

Autonomous control of flapping winged MAVs is a complex undertaking because of
the non-linear flight dynamics as presented
in~\cite{humbert:dipteran2}\cite{cheng:tandrdamping}. Although the dynamics of
flapping-winged flight can be averaged with respect to the wingbeat period as
presented in~\cite{Schenato:flightcontrol}\cite{cheng:tandrdamping}, we develop a
linear, one-dimensional model to predict the behavior of the system, similar
to~\cite{Shigeoka:ornithopter}. In addition to the nonlinearities, the system
is underactuated due to size constraints. Many of the methods for controlling
these platforms make extensive use of GPS in outdoor environments [CITATIONS]
and expansive motion capture systems in indoor environments. While operating
indoors, using GPS to estimate the pose of the MAV is not possible, and motion
capture requires expensive and stationary modification of the environment. The
power and payload limits on MAVs make on-board sensing difficult, so
multi-agent cooperative control schemes are apt solutions.

Many of the control laws that previous researches have developed from the
dynamic models of flapping-winged flight, such as periodic forcing and other
control methods as described %TODO you need to use real names, it's not kosher to refer to citation numbers directly
in~\cite{doman:dynamics}\cite{khan:longitudinal_control}\cite{leonard:averaging}, are computationally complex and
require powerful on-board computing. In our work, we develop a simpler, less
computationally intensive method of control for negotiating narrow passages.

@@

\subsubsection{Reachability Model}
%TODO make these span the page, with identical scales/style
